Rasterizing prodution per each region

### 2021-04-23 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
rasterized production for food systems run

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

@@

CHN:HKG
CHN:MAC
ESP:MAR
ESP:PRT
HKG:CHN
HRV:BIH
HRV:MNE
HRV:SVN
IDN:PNG
IRL:GBR
JPN:RUS
KHM:VNM
MEX:USA
MYS:BRN
MYS:THA
NLD:BEL
NLD:DEU
PRK:RUS
PRT:ESP
SVN:ITA
THA:MMR
THA:MYS
TWN:CHN
USA:CAN
USA:MEX
VNM:KHM

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:MAR", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:MAR", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ESP:FRA", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:FRA", "Spain", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:BIH", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:BIH", "Croatia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:MNE", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:MNE", "Croatia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HRV:SVN", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "JPN:RUS", "JPN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "JPN:RUS", "Japan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:BEL", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:BEL", "Netherlands", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRK:RUS", "PRK", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:ITA", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:ITA", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:MEX", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:MEX", "United States", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

@@

test <- farms_prod %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

>>>>

all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

@@

# CHN:HKG
# CHN:MAC
# ESP:FRA
# ESP:MAR
# ESP:PRT
# HKG:CHN
# HRV:BIH
# HRV:MNE
# HRV:SVN
# IRL:GBR
# JPN:RUS
# KHM:VNM
# MYS:BRN
# MYS:THA
# NLD:BEL
# NLD:DEU
# PRK:RUS
# PRT:ESP
# RUS:POL
# SVN:ITA
# THA:MMR
# THA:MYS
# TWN:CHN
# USA:CAN
# USA:MEX
# VNM:KHM

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:MAR", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:MAR", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ESP:FRA", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:FRA", "Spain", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:BIH", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:BIH", "Croatia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:MNE", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:MNE", "Croatia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HRV:SVN", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:BEL", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:BEL", "Netherlands", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRK:RUS", "PRK", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "RUS:POL", "RUS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "RUS:POL", "Russia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:ITA", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:ITA", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:MEX", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:MEX", "United States", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

@@

test <- farms_prod %>%
  st_drop_geometry() %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

### 2021-04-23 marine/shrimp/shrimp_farms/STEP4_rasterize_production.Rmd
rasterized production for food systems run

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:NIC", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:NIC", "Costa Rica", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ECU:COL", "ECU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ECU:COL", "Ecuador", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:HND", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:HND", "Guatemala", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:MEX", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:MEX", "Guatemala", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "MEX:GTM", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:GTM", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "PER:ECU", "PER", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PER:ECU", "Peru", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SLV:HND", "SLV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SLV:HND", "El Salvador", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

>>>>

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:NIC", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:NIC", "Costa Rica", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ECU:COL", "ECU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ECU:COL", "Ecuador", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:HND", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:HND", "Guatemala", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:MEX", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:MEX", "Guatemala", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "MEX:GTM", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:GTM", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MMR:THA", "MMR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "PER:ECU", "PER", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PER:ECU", "Peru", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SLV:HND", "SLV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SLV:HND", "El Salvador", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

### 2021-04-23 marine/tuna/tuna_farms/STEP4_rasterize_production.Rmd
rasterized production for food systems run

test <- farm_production %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

>>>>

test <- farm_production %>%
  st_drop_geometry() %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)
